\section{Related Work} 
\label{sec:related_work}

There has been a large amount of research in the area of procedural terrain generation. Traditionally most of it has focused on generating terrains by using fractal techniques, like Olsen's \cite{lechner:2006}, Szeliski and Terzopoulos's \cite{szeliski:1989}, and Pi's \cite{pi:2006}.

Olsen \cite{lechner:2006} discussed the use of fractal Brownian motion and perturbed Voronoi diagrams in erosion algorithms. Szeliski and Terzopoulos's \cite{szeliski:1989} used real digital elevation data, which they perturbed using splines to address fractal terrain generation. Pi \cite{pi:2006} created fractal landscapes using the Perlin noise algorithm. As with most fractal-based approaches, their algorithms did not appear to be controllable.

Li, Wang, Zhou, Tang, Yang \cite{li:2006} used machine learning to model example height maps. These models were then used to come up with new interesting terrains. Unfortunately, there was a major issue with this approach. There was a frequent unclearness of what needed to be learned or what features were important to be part of the training data.

Ong \cite{ong:2005} used genetic algorithms to generate terrains. Besides focusing on controllability, Ong's approach sketched the boundary of the terrain to be generated. The main form of controllability of this approach was a database containing a set of representative height map samples that could be controlled by the designer.
  
Lastly, Doran and Parberry \cite{doran:2010} focused on allowing the designers to have a more natural control over the generated terrains without sacrificing the desirable Procedural Content Generation attributes to some extent, such as novelty, structure, interest, and speed.

The aim of this paper is to describe a system that combines three well-known terrain generation algorithms (i.e., Perlin Noise  \cite{perlin:2002}, Simplex Noise \cite{perlin:2001}, Diamond Square \cite{fournier:1982}), and a JavaScript 3D engine, called Three.js \cite{threeJS}, for generating natural looking terrains on the Web.

% section related_work (end)
